Home

### 2019-05-22 analysis/index.Rmd
restructure for workflowr

Welcome to my research website.

Click on this [link](defoliation-maps.html) to see my results.

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/pat-s/paper_hyperspectral/commits/master)  
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.5.0-brightgreen.svg)](https://cran.r-project.org/)   
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)

[Project Description](about.html)

# Results

[Report: Defoliation](defoliation-maps.html).

# 
Powered by [drake](https://github.com/ropensci/drake) + [workflowr](https://github.com/jdblischak/workflowr) and [mlr](https://github.com/mlr-org/mlr)
